\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-25 paper.tex
Reword trading model

\subsubsection{Registrar}
Registrars have access to create and maintain Registration Contracts, a lookup table of participants in decentralized data marketplace.

@@

Brokers certify session keys as well. Only one session key can be signed in each product, so data providers cannot fake a session key to deceive consumers. When a data provider asks a broker to certify new session key $k$, the data provider uses the broker's public key, which is available in the Registration Contract after the broker's registration, as a blinding factor, and the session key is blinded. Then the data provider sends the blinded session key $Blind(k)$ to the broker. The broker signs the message and returns the signature $Sign(Blind(k))$ to data provider. The data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

@@

The contract address and product description will be stored in a file which is uploaded to IPFS. Consumers can search the desired product by keywords or tags. The consumer then evaluates the product and initiates the trading with the data provider if the consumer is interested in subscribing to the data.

\subsection{Trading}
Once a consumer who wants to subscribe certain streaming data that is generated  pays a subscription fee to the product contract, he/she is added to the consumers list automatically by the smart contract.

Next, session key $k$ should be exchanged between the data provider and consumers. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the product contract. Consumers decrypt the ciphertext from the product contract to obtain the session key $k$ and signature $Sign(k)$. Consumers can verify that the signature is valid and the session key is the only one that is certified by the broker. Afterward, encrypted data is published to the MAM channel, and consumers can obtain and decrypt it with the session key.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaciton among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing. We employed repeated games to build our game theory model. Repeated games fits the scenario of data subscription.

>>>>

\subsubsection{Registrar}
Registrars have access to create and maintain registration contracts, a lookup table of participants in decentralized data marketplace.

@@

Brokers certify session keys as well. Only one session key can be signed for each product, so data providers cannot fake a session key to deceive consumers. To certify a session key $k$, the data provider first blinds the session key with broker's public key from registration contract and sends $Blind(k)$ to the broker. The broker signs it and returns the signature $Sign(Blind(k))$ back, then the data provider removes the blinding factor and obtains the broker's signature of the session key, $Sign(k)$, which is verifiable by consumers.

@@

The contract address and product description will be stored in a file which is uploaded to IPFS. Consumers can search the desired product by keywords or tags and then launch a trading process for interested products.

\subsection{Trading}
Once a consumer subscribe to certain streaming data that is generated pays a subscription fee to the purchase contract, he/she is added to the consumers list automatically by the smart contract.

Next, session key $k$ should be exchanged between the data provider and consumers. For each consumer, the data provider encrypts the session key and broker's signature with the consumer's public key and sends the ciphertext $Encrypt(k + Sign(k))$ to the purchase contract. Consumers can decrypt $Encrypt(k + Sign(k))$ to obtain and verify the session key $k$ and signature $Sign(k)$. Afterward, consumers can access data with session key on the MAM channel.

@@

\subsection{Game Theory Evaluation}
Game Theory is a methodology to discuss strategic interaction among game players. If we can ensure Nash Equilibrium of decentralized data marketplace exists at a certain acceptable range, then we can promise the sustainability of decentralized data marketplace. Fan Liang et al\cite{SurveyBigDataPricing} listed several different types of game theory models which are applied to data pricing. We employed repeated games to build our game theory model. Repeated games fits the scenario of data subscription.
